Computing Vowel Elision in Yoruba Collocations

### 2023-04-14 paper.tex
Discuss SyllabifiedCandidate, deletion implementation. Add impl for ONSET

\usepackage{caption}
\usepackage{graphicx}
\usepackage{tipa}
\usepackage{ot-tableau}
\usepackage[margin=1in]{geometry}
\usepackage{minted}

@@

TODO: describe the algorithm succinctly using an algorithm figure?

@@

>>>>

\usepackage{caption}
\usepackage{graphicx}
\usepackage{tipa}
\usepackage{ot-tableau}
\usepackage[margin=1in]{geometry}
\usepackage{minted}
\usepackage{hyperref}

@@

@@

\begin{figure}[h]
\caption{Our representation of words in Yoruba, along with our strategy for deletion.}
\label{fig:impl-deletion}
\begin{minted}{rust}
#[derive(Debug, Clone)]
struct SyllabifiedCandidate {
    form: Vec<Segment>,
    rng: StdRng,
}

impl SyllabifiedCandidate {
    fn delete(mut self) -> Self {
        if !self.form.is_empty() {
            self.form.remove(self.rng.gen_range(0..self.form.len()));
        }
        self
    }
}
\end{minted}
\end{figure}

We now describe key details of our implementation. The full source code may be
found at \href{https://github.com/hemantgouni/linguistics-capstone}{github.com/hemantgouni/linguistics-capstone}.
Starting with the basics, Figure \ref{fig:impl-deletion} shows both our
representation of Yoruba words, and our simple handling of deletion.
Specifically, a word is represented as a list of segments (this is the meaning of
\texttt{Vec<Segment>}). At this point, you might ask: why not represent words simply
as a list of characters? What's the difference between a character and a segment?
This reflects a complication in computers' handling of text beyond simple English
characters, covered by the ASCII character encoding. Unicode, an improvement of
ASCII that handles many more languages beyond those which use the Latin alphabet,
would consider the accent mark and letter \textipa{O} in \textipa{\'O}, to be
separate characters, and not part of the same. We must sidestep this issue by
parsing words into \textit{graphemes}, which accounts for the intuitive notion
of what a character is.

With that technical hiccup out of the way, our implementation of deletion is much
simpler. It is interesting to note that within the context of our analysis,
deletion turns out to be the most important of the operations to implement, because
winning candidates are always generated via deletion (due to high-ranking \dep{}
and \ident{} constraints). We implement deletion by picking a random element of
the list of segments and removing it. Because we cluster characters by Unicode
graphemes, the probability of any single character being deleted is evenly
distributed between all in a given word.

\begin{figure}[h]
\caption{Our implementation of \onset}
\label{fig:impl-onset}
\begin{minted}{rust}
impl Constraint for Onset {
    fn evaluate(self, surface: SyllabifiedCandidate) -> usize {
        let syllabi = surface
            .form
            .iter()
            .filter(|seg| seg.syllable_index == SyllableIndex::Nucleus)
            .count();

        let onsets = surface
            .form
            .iter()
            .filter(|seg| seg.syllable_index == SyllableIndex::Onset)
            .count();

        onsets - syllabi
    }
}
\end{minted}
\end{figure}

We now
